Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-11-18 analysis/paper/paper.Rmd

---
title: "Change in Mobility and Site Occupation during the Late Pleistocene in Korea"
author:
  - Author Gayoung Park!
  - Author Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  According to Human Behavioral Ecology, stone artifacts can be an essential source of information for understanding hunter-gatherer subsistence. We examine stone artifacts from 22 sites in Korea to investigate a change in mobility and site occupation during the Late Pleistocene. The new technology is represented by the technological change, the appearance of stemmed points, and the following blade industry. The overall aim is to understand how the appearance of stemmed points affected hunter-gatherers in Korea, which leads to three specific questions to pursue: how did the introduction of the new tools change the way people used the landscape, the way people used sites, and the population. Based on the hypothesis that hunter-gatherers should move frequently and further in order to adapt to a changing environment, so their tools became more portable and efficient, as indicated by decreases in toolkit size and increases in function and utility, we analyze artifact density, retouch frequency, radiocarbon dates, elevation of the sites, raw material types, and composition of the toolkit. The results show that the new technology enabled the occupation of marginal environments at higher elevations. There is no strong general relationship between technology and ecological change. Instead, we assume that population dynamics might have had more impact on changes in stone artifact technology and hunter-gatherer subsistence. 
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

>>>>

---
title: "Change in Mobility and Site Occupation during the Late Pleistocene in Korea"
author:
  - Author Gayoung Park!
  - Author Ben Marwick!
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  According to Human Behavioral Ecology, stone artifacts can be an essential source of information for understanding hunter-gatherer subsistence. We examine stone artifacts from 22 sites in Korea to investigate a change in mobility and site occupation during the Late Pleistocene. The new technology is represented by the technological change, the appearance of stemmed points, and the following blade industry. The overall aim is to understand how the appearance of stemmed points affected hunter-gatherers in Korea, which leads to three specific questions to pursue: how did the introduction of the new tools change the way people used the landscape, the way people used sites, and the population. Based on the hypothesis that hunter-gatherers should move frequently and further in order to adapt to a changing environment, so their tools became more portable and efficient, as indicated by decreases in toolkit size and increases in function and utility, we analyze artifact density, retouch frequency, radiocarbon dates, elevation of the sites, raw material types, and composition of the toolkit. The results show that the new technology enabled the occupation of marginal environments at higher elevations. There is no strong general relationship between technology and ecological change. Instead, we assume that population dynamics might have had more impact on changes in stone artifact technology and hunter-gatherer subsistence. 
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---
